Explaining NonLinear Classification Decisions with Deep Taylor Decomposition\\ analysis

### 2022-05-29 Präsentation/Präsentation_23.06.2020.tex
presentation

\usetheme{CambridgeUS}
\usepackage{ngerman}

\begin{document}
\title[Deep Taylor Decomposition]{Explaining NonLinear Classification Decisoins with Deep Taylor Decomposition\\
an anlysis}  
\author{Marcel Pommer}
\institute{LMU M\''unchen}
\date{\today}

@@

\begin{frame}
\frametitle[Inhaltsverzeichnis]{Inhaltsverzeichnis}
\vspace{0.4cm}
\tableofcontents
\end{frame}

\AtBeginSection[]
{
\begin{frame}
\frametitle[Inhaltsverzeichnis]{Inhaltsverzeichnis}
\vspace{0.4cm}
\tableofcontents[currentsection]
\end{frame} 
}

\section{Das Modell} 
\begin{frame}
\frametitle{Das Modell} 
\vspace{0.3cm}
\begin{itemize}
\item Eine Ma{\ss}nahme ``0'' oder ``1'' muss getroffen werden.
\item Die gew\"unschte Ma{\ss}nahme ist abh\"angig vom Zustand $\omega \in \{0,1\}$, wobei $\omega$ mit gleicher Wahrscheinlichkeit den beiden Zust\"anden entspricht.
\item Jeder Agenten aus $N=\{1,...,n\}$, $n\geq 3$, $n$ ungerade erh\"alt ein Signal $x_i$, welches mit der Wahrscheinlichkeit $\frac{1}{2}<p<1$ dem Zustand $\omega$ entspricht.
\item Ziel ist die Implementierung der gew\"unschten Ma{\ss}nahme. Gegeben $K$ Signalen entspricht dies:
\begin{flalign*}
\hspace{-1cm}
V(K)&=Prob\textnormal{\{strikte Mehrheit der Agenten erh\"alt das korrekte Signal\}}\\
&+ \frac{1}{2} Prob\textnormal{\{H\"alfte der Agenten erh\"alt das korrekte Signal\}}
\end{flalign*}
\item F\"ur obige Nutzenfunktion gilt $V(2k-1)=V(2k)<V(2k+1)$.
\end{itemize}
\end{frame}

\subsection{Beweis: $V(2k-1)=V(2k)$}
\begin{frame}\frametitle{Beweis von $V(2k-1)=V(2k)$} 
\scriptsize
\begin{flalign*}
V(2k)&=\sum_{i=0}^{k-1}\binom{2k}{i}p^{2k-i} (1-p)^i + \frac{1}{2}\binom{2k}{k}p^k(1-p)^k\\
&=p^{2k} + \sum_{i=1}^{k-1}\binom{2k-1}{i}p^{2k-i}(1-p)^i + \sum_{i=1}^{k-1}\binom{2k-1}{i-1}p^{2k-i}(1-p)^i + \frac{1}{2}\binom{2k}{k}p^k(1-p)^k\\
&=p\cdot \sum_{i=0}^{k-1}\binom{2k-1}{i}p^{2k-1-i}(1-p)^i+\sum_{i=1}^{k-1}\binom{2k-1}{i-1}p^{2k-i}(1-p)^i + \frac{1}{2}\binom{2k}{k}p^k(1-p)^k\\
&=p\cdot V(2k-1)+(1-p)\sum_{i=0}^{k-2}\binom{2k-1}{i}p^{2k-1-i}(1-p)^i+ \frac{1}{2}\binom{2k}{k}p^k(1-p)^k\\
&=p\cdot V(2k-1) + (1-p)\biggl[\sum_{i=0}^{k-1}\binom{2k-1}{i}p^{2k-1-i}(1-p)^i-\binom{2k-1}{k-1}p^k(1-p)^{k-1}\biggl]\\
&+ \frac{1}{2}\binom{2k}{k}p^k(1-p)^k\\ 
&=p\cdot V(2k-1) + (1-p)\cdot V(2k-1) - \binom{2k-1}{k-1}p^k(1-p)^k+\frac{1}{2}\binom{2k}{k}p^k(1-p)^k\\
&=V(2k-1)
\end{flalign*}

@@

\subsection{Zwei m\"ogliche Mechanismen}
\begin{frame}\frametitle{Zwei m\"ogliche Mechanismen} 
\begin{enumerate}
\item \textbf{Der direkte simultane Mechanismus:} Alle Agenten sprechen ihre Empfehlung simultan aus, die Mehrheit entscheidet.
\item \textbf{Der F\"uhrer Mechanismus:} Die Agenten $\{1,...,n-1\}$ sprechen simultan ihre Empfehlung aus, welche an Agent $n$ weitergegeben werden. Dieser entscheidet anhand der Empfehlungen der anderen Agenten und seines eigenen Signals, welche Ma{\ss}nahme getroffen wird.
\end{enumerate}
\begin{itemize}
\item Ein Mechanismus implementiert das \"offentliche Ziel, falls f\"ur jedes sequentielle Gleichgewicht gilt $\pi_1=V(n)$, wobei $\pi_1$ als die Wahrscheinlichkeit definiert ist, dass die gew\"unschte Ma{\ss}nahme getroffen wird.
\end{itemize}
\end{frame}

@@

\subsection[Proposition 1]{Beweisidee Proposition 1}
\begin{frame}\frametitle{Proposition 1}
\begin{block}{Proposition 1}
``In einer Gesellschaft, in der alle Agenten ausschlie{\ss}lich am Allgemeinwohl interessiert sind, hat jeder Mechanismus ein sequentielles Gleichgewicht indem $\pi_1\leq V(1)$.''[GR98]
\end{block}
\end{frame}

\begin{frame}\frametitle{Beweisidee von Proposition 1}

\begin{enumerate}
\item Zun\"achst betrachte einen Mechanismus mit einem Schritt: 
\begin{itemize}
\item Falls das Ergebnis konstant ist, gilt $\pi_1=V(0)$.
\item Falls das Ergebnis nicht konstant ist, gibt es einen Agenten $i$, sodass die getroffene Ma{\ss}nahme von seinem Signal abh\"angt. Jedem Agenten $j\neq i$ wird eine Aktion $a_j$, unabh\"angig seines Signals, zugeordnet, sodass das Ergebnis nur vom Signal von Agent $i$ abh\"angig ist.
\item[$\rightarrow$] Kein Agent kann profitabel abweichen, da $V(1)=V(2)$.
\end{itemize}
\item Ein Mechanismus mit zwei Schritten:
\begin{itemize}
\item Falls das Ergebnis nach dem ersten Schritt bereits feststeht, handelt es sich um einen Mechanismus mit einem Schritt.
\item Falls nicht, weise, wie oben erkl\"art, jedem Agenten im zweiten Schritt eine Aktion zu, sodass das Ergebnis nur vom Signal eines Agenten abh\"angig ist.
\item Weise zudem jedem Agenten im ersten Schritt eine Aktion, unabh\"angig vom Signal zu, sodass der erste Schritt eine Teilgeschichte vom zweiten Schritt ist.
\end{itemize}
\end{enumerate}
\end{frame}

\section[Das PT und das private Motiv]{Die Implementierung des PT ist m\"oglich, wenn alle Agenten neben dem Allgemeinwohl auch ihr privates Interesse verfolgen}
\subsection{Der Mechanismus}
\begin{frame}\frametitle{Der Mechanismus}
\textbf{Das private Motiv:} Alle Agenten sind neben dem Allgemeinwohl auch daran interessiert, $\pi_{2,i}$, die Wahrscheinlichkeit, dass Ihre Empfehlung mit der getroffenen Ma{\ss}nahme \"ubereinstimmt, zu maximieren.
\vspace{0.5cm}

\textbf{Schritt 1:} Agent 1 (``controller'') bestimmt eine Menge $S$ von Agenten, wobei $S$ gerade und Agent 1 nicht Teil der Menge $S$ ist.

Gleichzeitig geben alle Agenten bis auf Agent 1 simultan ihre Empfehlung ab.

\textbf{Schritt 2:} Agent 1 erf\"ahrt das Abstimmungsergebnis aus der Menge $S$ und gibt seine eigene Stimme ab.
\begin{itemize}
\item[$\rightarrow$]Die Mehrheit aus $S \cup \{1\} $ entscheidet \"uber die Ma{\ss}nahme.
\end{itemize}
\end{frame}

\subsection{Proposition 2}
\begin{frame}\frametitle{Proposition 2}
\begin{block}{Proposition 2}
``In einer Gesellschaft, in der alle Agenten strikt positive Pr\"aferenzen bez\"uglich dem Allgemeinwohl und ihrem privatem Motiv haben, implementiert obiger Mechanismus das PT, es gilt $\pi_1=V(n)$ f\"ur jedes sequentielle Gleichgewicht.''[GR98]\\
Agent 1 w\"ahlt $S=N \setminus \{1\}$, alle Agenten $i\in \{2,...,n\}$ spielen ``T'', Agent 1 folgt der Mehrheit und spielt im Fall eines Unentschieden selber ``T''.
\end{block}
\end{frame}

\subsubsection{Hilfslemma 1}
\begin{frame}\frametitle{Hilfslemma 1}
\begin{block}{Hilfslemma 1}
 Sei $S$ eine Teilmenge aller Agenten und ungerade und sei $s_i=0$ die Strategie von Agent $i$. Zudem sei $N_x$ die Anzahl Agenten, die die Strategie $x\in \{``T\dq,``0\dq,``1\dq\}$ verfolgen. \\
\textbf{Behauptung:} Falls $N_0>N_1$, f\"uhrt ein Wechsel der Strategie von Agent $i$ zu ``T'' zu einer Erh\"ohung von $\pi_1$. Falls $N_0=N_1$, beeinflusst ein Wechsel von Agent $i$ zur Strategie ``T'' $\pi_1$ nicht.
\end{block}
\end{frame}

\begin{frame}\frametitle{Beweis Hilfslemma 1}
\textbf{Beweis:} Ich nutze, dass ``c'' mit der Wahrscheinlichkeit $\frac{1}{2}$ dem Zustand $\omega$ entspricht.
\begin{flalign*}
V(2k) \cup ``c\dq  &= \frac{1}{2}\sum_{i=0}^{k}\binom{2k}{i}p^{2k-i}(1-p)^i + \frac{1}{2}\sum_{i=0}^{k-1}\binom{2k}{i}p^{2k-i}(1-p)^i\\
&=\sum_{i=0}^{k-1}\binom{2k}{i}p^{2k-i}(1-p)^i + \frac{1}{2}\binom{2k}{k}p^{2k-i}(1-p)^i\\
&=V(2k)\\
&=V(2k-1)\\
&<V(2k+1)
\end{flalign*}
\end{frame}

\subsubsection{Beweisidee Proposition 2}
\begin{frame}\frametitle{Beweisidee Proposition 2}
\begin{enumerate}
\item Agent 1 w\"ahlt $S$, sodass $S_{NT}=\varnothing$.
\item [$\rightarrow$] folgt, da $V(2k-1)=V(2k)<V(2k) \cup ``NT\dq$
\item Agent 1 w\"ahlt $S$, sodass $\vert \vert S_0 \vert - \vert S_1 \vert \vert = k \leq 1$.
\item [$\rightarrow$] falls $k>1$, ist das Ergebnis in eine Richtung beeinflusst
\item Mit Hilfslemma 1 folgt, dass $k=0$. Es gibt einen Agenten $i \in S_c$, der durch ein Abweichen auf ``T'' $\pi_1$ und $\pi_{2,i}$ erh\"oht.
\item Mit Hilfslemma 1 folgt, $S_c=\varnothing$. Jeder Agent $i \in S_c$ kann durch ein Abweichen $\pi_{2,i}$ erh\"ohen, ohne $\pi_1$ zu beeinflussen.
\item Jeder Agent $i \notin S$ spielt ``T'', da seine Srategie $\pi_1$ nicht beeinflusst, aber dadurch $\pi_{2,i}$ maximiert wird.
\item [$\rightarrow$] Es folgt, dass $S=\{2,...,n\}$ und alle Agenten in $S$ ``T'' spielen. Agent 1 folgt der Mehrheit und im Fall eines Unentschieden, spielt er ``T''.
\end{enumerate}
\end{frame}

>>>>

\usetheme{CambridgeUS}
\usepackage{ngerman}
\renewcommand{\figurename}{Figure}
\renewcommand{\tablename}{Tabel}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

\begin{document}
\title[Deep Taylor Decomposition]{Explaining NonLinear Classification Decisions with Deep Taylor Decomposition\\
analysis}  
\author{Marcel Pommer}
\institute{LMU M\"unchen}
\date{\today}

@@

\begin{frame}
\frametitle[Explainability]{Explainability}
\begin{center}
\includegraphics[width=0.9\textwidth]{image/introduction_image}
\end{center}
\vspace{0.25cm}
Deep neural networks have great performance on a variety of problems \\
\textbf{but} how can we justify decisions made by complex deep architectures?\\
\end{frame}

\begin{frame}
\frametitle[Table of Contents]{Table of Contents}
\vspace{0.4cm}
\tableofcontents
\end{frame}

\AtBeginSection[]
{
\begin{frame}
\frametitle[Table of Contents]{Table of Contents}
\vspace{0.4cm}
\tableofcontents[currentsection]
\end{frame} 
}

\section[Introduction]{Introduction}
\begin{frame}
\frametitle{Introduction} 
\textbf{Deep neural networks revolutionized amongst others the field of}\\
\vspace{0.25cm}
       \begin{columns}[T]
          \column{0.65\textwidth}
             \centering
             \includegraphics[height=5cm, width=8cm]{image/NLP_chatbot}
           \column{0.35\textwidth}
			\begin{itemize}
			\item[--] Image recognition
			\item[--] Natural language processing
			\item[--] Human action recognition
			\item[--] Physics
			\item[--] Finance
			\item[--] ...
			\end{itemize}
         \end{columns} 
\vspace{0.5cm}
With one major drawback $\rightarrow$ \textbf{lack of transparency}
\end{frame}

\subsection[interpretable classifier]{Interpretable Classifier}
\begin{frame}
\frametitle{Interpretable Classifier} 
\vspace{0.5cm}
Explanation of non-linear classification in terms of the inputs\\
$\rightarrow$ A classifier should not only provide a result but also a reasoning

\begin{center}
\includegraphics[height=5cm, width=8cm]{image/cancer}
\end{center}

We do not only need to know if the patient has cancer but also where exactly it is located

@@

\subsection[General Idea]{General Idea}

\begin{frame}
\frametitle{General Idea} 
\vspace{0.35cm}
To accomplish the task of explainability we map relevance from the output to the input features

\vspace{0.25cm}

\begin{center}
\begin{figure}
\includegraphics[height=4.5cm, width=11cm]{image/fig._1_example}
\caption{NN detecting 0 while distrected by 5}
\end{figure}
\end{center}

\section[Pixel-Wise Decomposition]{Pixel-Wise Decomposition}

\subsection[Mathematical Framework and Definitions]{Mathematical Framework and Definitions}

\begin{frame}
\frametitle{Mathematical Framework}
\vspace{0.5cm} 
In the context of image classification we define the following mathematical framework
\begin{itemize}
\item Positive valued function $f:\mathbb{R}^d\to \mathbb{R}^+$, where the output $f(x)$ defines either the probability that the object is present or the quantity of the object in question
\item[$\rightarrow$] $f(x)>0$ expresss the presence of the object  
\item Input $x \in \mathbb{R}^d$, composable in a set of pixel values $x=\{x_p\}$
\item Relevance score $R_p(x)$ indicating the relevance of each pixel
\item[$\rightarrow$] The relevance score can be displayed in a heatmap denoted by $R(x) = \{R_P(x)\}$
\end{itemize}

\begin{figure}
\includegraphics[height=2cm, width=2cm]{image/heatmap_example}
\end{figure}

\begin{frame}
\frametitle{Definitions}
\begin{block}{Definition 1}
A heatmapping $R(x)$ is \underline{conservative} if the sum of assigned relevances in the pixel space corresponds to the total relevance detected by the model, that is
\begin{equation}
\forall x: f(x)=\sum_pR_p(x)
\end{equation}
\end{block}

\begin{block}{Definition 2}
A heatmapping $R(x)$ is  \underline{positive} if all values forming the heatmap are greater or equal to zero, that is:
\begin{equation}
\forall x,p: R_p(x) \geq 0
\end{equation}
\end{block}

\begin{frame}
\frametitle{Definitions}
Further we test all algorithms for compliance with definition 1 and 2 why we introduce the definition of consistency which forth on is a measure of correctness of a technique\\
%\vspace{0.1cm}

\begin{block}{Definition 3}
A heatmapping $R(x)$ is  \underline{consistent} if it is  \textit{conservative} and  \textit{positive}. That is, it is consistent if it complies with Definitions 1 and 2.
\end{block}

\vspace{0.5cm}
However consistency is not a measure of quality which can be seen easily on the following example which complies with definition 3
\begin{equation*}
\forall p: R_p(x) =\frac{1}{d} \dot f(x) ,
\end{equation*}
where d denotes the number of pixels
\end{frame}

\subsection[Methodology]{Methodology}

\begin{frame}
\frametitle{Taylor Expansion}
\vspace{0.35cm}
First order taylor expansion at root point $\tilde{x}$
\begin{flalign*}
 f(x) & =f(\tilde{x}) + \left( \frac{\partial f}{\partial x}\Big|_{x=\tilde{x}}\right)^T \cdot (x-\tilde{x}) + \epsilon\\
       & = 0 + \sum_p \underbrace{\frac{\partial f}{\partial x_p}\Big|_{x=\tilde{x}} \cdot (x_p-\tilde{x_p})}_{R_p(x)} + \epsilon  
\end{flalign*}
The challenge of finding a root point
 \begin{columns}
          \begin{column}[T]{5.5cm}
             \begin{figure}
             \includegraphics[height=2.75cm, width=6cm]{image/fig._2_example_root_point}
             \end{figure}
            \end{column} 
            \begin{column}[T]{6.2cm}
			\begin{itemize}
			\item Potentially more than one root point
			\item Remove object but deviate as few as possible
			\item[$\rightarrow$] $\min_{\xi} ||\xi-x||^2 \text{ subject to } f(\xi)=0$
			\end{itemize}
	\end{column}
\end{columns}

\begin{frame}
\frametitle{Sensitivity Analysis}
Choose a root point at infinitisimally small distance from the actual point, i.e. $\xi = x- \delta \frac{\partial f}{\partial x}$\\
If we assume a locally constant function we get
\begin{flalign*}
 f(x) & =f(\xi) + \left( \frac{\partial f}{\partial x}\Big|_{x=\xi}\right)^T \cdot (x- (x- \delta \frac{\partial f}{\partial x})) + 0\\
       & = f(\xi) + \delta \left( \frac{\partial f}{\partial x}\right)^T  \frac{\partial f}{\partial x} + 0\\
       & = f(\xi) + \sum_p \underbrace{ \delta \left( \frac{\partial f}{\partial x}\right)^2}_{R_p} + 0
\end{flalign*}

\begin{itemize}
\item The heatmap is positive but not conservative
\item Measure local effect
\end{itemize}

\begin{frame}
\frametitle{Deep Taylor Decomposition}
\vspace{0.25cm}
\begin{figure}
\includegraphics[height=2.75cm, width=11cm]{image/deep_taylor_decomposition_example}
 \end{figure}
We view each layer as a seperate function and write the Taylor decomposition of $\sum_j R_j \text{ at } \{x_i\}$ as
\begin{align*}
    \sum_j R_j &= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\Big|_{\{\tilde{x_i}\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}\}) + \epsilon\\
    &= \sum_i \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x_i}) + \epsilon
\end{align*}

\begin{frame}
\frametitle{Deep Taylor Decomposition}
\vspace{0.25cm}
\begin{figure}
\includegraphics[height=2.75cm, width=11cm]{image/deep_taylor_decomposition_example}
 \end{figure}

\begin{itemize}
\item  If each local Taylor decomposition is \textit{conservative} then the chain of equalitis is also \textit{conservative} (Layer-wise relevance conservation)
\item[$\rightarrow$] $R_f = ...= \sum_i R_i = ... = \sum_p R_p$
\item  If each local Taylor decomposition is \textit{positive} then the chain of equalitis is also \textit{positive} 
\item[$\rightarrow$] $R_f,...,\{R_i\},...,\{R_P\} \geq 0$
\item If each local Taylor decomposition is \textit{consistent} then the chain of equalitis is also \textit{consistent} 
\end{itemize}

\section[One-Layer Networks]{Application to One-Layer Networks and Root Finding}

\begin{frame}
\frametitle{Setting}
\vspace{0.2cm}
Consider a simple detection-pooling one layer neural network with
 \begin{columns}
          \begin{column}[T]{5.5cm}
		\begin{align*}
		x_j &= \max(0, \sum_i x_iw_{ij} + b_j)\\
		x_k &= \sum_j x_j, \ b_j \leq 0, \forall j
		\end{align*}
            \end{column} 
            \begin{column}[T]{6.5cm}
			\begin{figure}
				\includegraphics[height=2.5cm, width=6cm]{image/one_layer_nn}
			\end{figure}
	\end{column}
\end{columns} 
\begin{enumerate}
\item $R_k = x_k$ and thus $R_k = \sum_j x_j$
\item  Chose a root point and redistribute $R_k$ on neurons $x_j$\\
$\rightarrow$ $R_j = \frac{\partial R_k}{\partial x_j}\Big|_{\{\tilde{x}_j\}} \cdot (x_j - \tilde{x}_j) $, with $\{x_j\}=0$
\item Since $\frac{\partial R}{\partial x_j}=1$ we obtain $R_j = x_j$
\item Apply Taylor decomposition another time and get\\
 $R_i = \sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)})$
\end{enumerate}

\begin{frame}
\frametitle{Derivation of Propagation Rules}
Given $R_j = \max(0, \sum_i x_iw_{ij} + b_j)$ and $b_j <0$ and a search direction $\{v_i\}^{(j)}$ in the input space such that
\vspace{-0.35cm}
\begin{equation}
\{\tilde{x}\}^{(j)} = \{x_i\} + t \{v_i \} ^{(j)} \Leftrightarrow t = \frac{\tilde{x_i}^{(j)} - x_i}{v_i^{(j)}}
\label{equ:search_direction}
\end{equation}
\vspace{-0.35cm}

If the data point itself is not a root point, i.e. $\sum_i x_i w_{ij} + b_j>0$ the nearest root along $\{v_i\}^{(j)}$ is given by the intersection of equation \eqref{equ:search_direction} and $\sum_i\tilde{ x_i}^{(j)} w_{ij} + b_j=0$ which can be resolved to 
\vspace{-0.25cm}
\begin{align*}
0 &= \sum_i\{x_i\}w_{ij} + b_j + \sum_i v_i^{(j)} t \\
x_i - \tilde{x_i}^{(j)} & = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
\end{align*}

\begin{frame}
\frametitle{Derivation of Propagation Rules}
\vspace{0.4cm}
Starting from the Taylor expansion we can plug in 
\begin{align*}
x_i - \tilde{x_i}^{(j)} = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
\end{align*}
\vspace{-0.2cm}
To get
\vspace{-0.2cm}
\begin{align*}
R_i & = \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i^{(j)}} \dot (x_i - \tilde{x}_i^{(j)})= \sum_j w_{ij}\frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}\\
&= \sum_j w_{ij}\frac{v_i^{(j)} w_{ij}}{\sum_i v_i^{(j)} w_{ij}} R_j \numberthis \label{equ:relevance_model}
\end{align*}

The relevance propagation rule can now easily be calculated by defining
\begin{enumerate}
	\item Define a segment with search directio $\{v_i\}^{(j)}$
	\item The line lies inside the input domain and contains a root point
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}
\end{frame}

\subsection[$w^2$-rule]{$w^2$-rule}

\begin{frame}
\frametitle{$w^2$-rule $\mathcal{X}=\mathbb{R}^d$}
Choose root point which is nearest in euclidean sense\\
\begin{enumerate}
	\item Search direction $\{v_i\}^{(j)} = w_{ij}$
	\item No domain restriction
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}

\begin{block}{$w^2$-rule}
\begin{equation*}
R_i =\sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)}) =  \sum_j\frac{w_{ij}^2}{\sum_i w_{ij}^2} R_j
\end{equation*}
\end{block}

\begin{frame}
\frametitle{$w^2$-rule $\mathcal{X}=\mathbb{R}^d$}
\vspace{0.3cm}
\begin{block}{Proposition 1}
For all function $g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent.
\end{block}
\textbf{Proof}\\
\begin{enumerate}
\item \textit{Conservative}
\begin{align*}
\sum_i R_i &= \sum_i\Big(\sum_j \frac{w_{ij}^2}{\sum_iw_{ij}^2}R_j\Big)\\
   		&= \sum_j \frac{\sum_i w_{ij}^2}{\sum_iw_{ij}^2}R_j = \sum_j R_j = \sum_j x_j = f(x)
\end{align*}
\item \textit{Positive}
\begin{align*}
R_i = \sum_j \frac{w_{ij}^2}{\sum_i w_{ij}^2}R_j = \sum_j \underbrace{w_{ij}^2}_{>0}  \underbrace{\frac{1}{\sum_i w_{ij}^2}}_{>0}  \underbrace{R_j}_{\geq 0} \geq 0
\end{align*}
\end{enumerate}

\subsection[$z^+$-rule]{$z^+$-rule}

\begin{frame}
\frametitle{$z^+$-rule $\mathcal{X}=\mathbb{R}_+^d$}
\vspace{0.25cm}
Search for a root point on the segment $(\{x_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathbb{R}_+^d$\\
\begin{enumerate}
	\item Search direction $\{v_i\}^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$
	\item If $\{x_i\} \in \mathbb{R}_+^d$ so is the whole domain, further for $w_{ij}^-=\min(0,w_{ij})$
	\
	\begin{align*}
		R_j(\{x_i1_{w_{ij}<0}\}) = \max(0, \sum_i x_i 1_{w_{ij}<0} w_{ij} + b_j)\\
		= \max(0, \sum_i x_i  w_{ij}^- + b_j) = 0
	\end{align*}

	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}

\begin{block}{$z^+$-rule}
\begin{equation*}
R_i =  \sum_j \frac{x_i w_{ij}^+}{\sum_{i'} x_{i'} w_{i'j}^+} R_j
\end{equation*}
\end{block}

\begin{frame}
\frametitle{$z^+$-rule $\mathcal{X}=\mathbb{R}^d_+$}
\vspace{-0.4cm}
\begin{block}{Proposition 2}
For all function $g \in G$ and data points $\{x_i\} \in \mathbb{R}_+^d$, the deep Taylor decomposition with the $z^+$-rule is consistent.
\end{block}
\vspace{0.5cm}
\textbf{Proof}\\
If $\sum_i x_i w_{ij}^+ >0$ the same proof as for the $w^2$-rule applies, if $\sum_i x_i w_{ij}^+ =0$ follows that $\forall i: x_i w_{ij} \leq0$ and

\begin{align*}
 R_j = x_j = 0
\end{align*}
and there is no relevance to redistribute to the lower layers.

\subsection[$z^b$-rule]{$z^b$-rule}

\begin{frame}
\frametitle{$z^b$-rule $\mathcal{X}=\mathcal{B}$}
\vspace{0.4cm}
Often we have a bounded input space $\mathcal{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\} $ and a segment $(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathcal{B}$\\
\begin{enumerate}
	\item Search direction $\{v_i\}^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$
	\item If $\{x_i\} \in \mathcal{B}$ so is the whole domain, further for $w_{ij}^-=\min(0,w_{ij})$ and $w_{ij}^+=\max(0,w_{ij})$
	\vspace{-0.25cm}
	\begin{align*}
		R_j(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\}) &= \max(0, \sum_i l_i 1_{w_{ij}>0} w_{ij} + h_i 1_{w_{ij}<0} w_{ij} + b_j)\\
		&=\max(0, \sum_i l_i w_{ij}^+ + h_i w_{ij}^- + b_j)= 0
	\end{align*}
	\vspace{-0.25cm}
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}
\vspace{-0.25cm}

\begin{block}{$z^b$-rule}
\begin{equation*}
R_i =  \sum_j \frac{x_i w_{ij} - l_i w_{ij}^+ - h_i w_{ij}^-}{\sum_{i'} x_{i'} w_{i'j}  - l_i w_{i'j}^+ - h_i w_{i'j}^-} R_j
\end{equation*}
\end{block}

\begin{frame}
\frametitle{$z^b$-rule $\mathcal{X}=\mathcal{B}$}
\vspace{-0.4cm}
\begin{block}{Proposition 3}
For all function $g \in G$ and data points $\{x_i\} \in \mathcal{B}$, the deep Taylor decomposition with the $z^b$-rule is consistent.
\end{block}
\vspace{0.5cm}
\textbf{Proof}\\
Since the proof is similar to the proofs of proposition 1 and 2 but lenghty I refer to the literature.

@@
